---
title: "course_notes"
author: "baf44"
date: "4/2/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document will be used to take notes and code along with Coursera's Data Science: Foundations using R Specialization. 

### The Data Scientist's Toolbox: Week 4
## Markdown syntax
Some examples of Markdown code are:
**bold**
*italic*
--strikethrough--
[cheatsheet] (https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf)

## Types of Data Science Questions
* Descriptive data analysis
  + Goal: Describe or summarize a set of data
  + Early analysis when receive new data
  + Generate simple summaries about the samples and their measurements (e.g., means of central tendency and variance)
  + NOT for generalizing the results of the analysis to a larger population or trying to make conclusions
* Exploratory analysis
  + Goal: examine the data and find relationships that weren't previously known
  + Explore how different variables might be related
  + Useful for discovering new connections
  + Help to formulate hypotheses and drive the design of future studies and data collection
  + should not be used as a final say for how variables are related
* Inferential analysis
  + Goal: use a relatively small sample of data to say something about the population at large
  + Commonly the goal of statistical modeling
  + Provide your estimate of the variable for the population and provide your uncertainty about your estimate
  + Ability to accurately infer information about the larger population depends heavily on the sampling scheme -- if dataset is not representative of the population you are trying to make generalizations about, generalizations will not be accurate 
* Predictive analysis
  + Goal: use current and historical data to make predictions about future data
  + Accuracy in predictions is dependent on measuring the right variables
  + More date and a simple model generally perform well at predicting future outcomes
  + Prediction does not mean a causal mechanism
* Causal analysis
  + Goal: see what happens to one variable when we manipulate another variable
  + Gold standard in data analysis
  + Often applied to the results of randomized studies that were designed to identify causation; difficult to do with observational data
  + Usually analyzed in aggregate and observed relationships and are usually average effects
* Mechanistic analysis
  + Goal: understand exact changes in variables that lead to exact changes in other variables
  + Applied to simple sitations or those that are nicely modeled by deterministic questions
  + Commonly applied to physical or engineering sciences -- bio sciences are too noisy
  + Often, the only noise in the data is measurement error, which can be accounted for

# Data sharing guide
https://github.com/jtleek/datasharing

## Big data
* Volume, velocity (collected fast), variety  
* Sometimes need to work with unstructured data (e.g., text documents, websites)  
* Challenges: lots to store and analyze, constantly updating, messy, what source and type of data is best?
* Benefits: lots of data negates small errors, can do real time analyses, can answer unconventional questions, hidden correlations can be resolved

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
